% Welcome to the simple DIS curriculum vitae template!
% Please delete any sections that do not apply to your past experiences. We do not expect that applicants will have itmes for all of the sections included here. You can also rename or revise sections to best fit with your personal accomplishments.
% The final document should not exceed 3 pages

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, % set true if you want colored links
    linkcolor=blue,  % choose some color if you want links to stand out
    urlcolor=blue,   % choose some color for URLs
    citecolor=blue   % choose some color for citations
}
\usepackage{fancyhdr}
\usepackage{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{fontawesome5}
\input{glyphtounicode}

\usepackage[sfdefault]{inter} 
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\setlength{\footskip}{10pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{0.0in}
\addtolength{\evensidemargin}{0.0in}
\addtolength{\textwidth}{0.0in}
\addtolength{\topmargin}{0.2in}
\addtolength{\textheight}{0.0in}


\urlstyle{same}

%\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \it\vspace{3pt}
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-10pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\begin{document}


\begin{center}
    {\huge \textbf{Aritra Bhattacharya}} \\ \vspace{0pt}
    \begin{multicols}{2}
    \begin{flushleft}
    \large{Department of Biology,} \\
%  optional line below if you need more address info
    \large{Texas A\&M University,} \\
    \large{424 Nagle St, College Station} \\
    \large{77840, Texas, USA} \\
    \end{flushleft}
    
    \begin{flushright}
% below could be LinkedIn, GitHub, or a personal website or social media account (if used for professional purposes)
    \faGlobe\large{ \href{https://aritra-evolves.github.io/}{aritra-evolves.github.io}} \\
% please ensure your email address is one you check
    \faAt\large{ \href{mailto:ecoevoaritra23@tamu.edu}{ecoevoaritra23@tamu.edu}} \\
    \faAt\large{ \href{mailto:aritra.evolves@gmail.com}{aritra.evolves@gmail.com}} \\
    \faPhone*\large{+1 (979) 422-6110}
    \end{flushright}
    \end{multicols}
\end{center}


%-----------EDUCATION-----------
% Please list your current institution first and then past schools in reverse chronology. No need for grades, etc. You do not need to include high school but may do so if there are accomplishments you would like to highlight.
\section{Education}
\resumeSubHeadingListStart

    \resumeSubheading
% list month-year for the start date followed by month-year for the end date (or "Present" if in progress)
{Texas A\&M University}{August 2023 -- Present}
        {PhD in Biology}{College Station, Texas, USA}
    \resumeSubheading
        {Maulana Abul Kalam Azad University of Technology, WB }{ November 2020 -- June 2022}
        {MSc in Biotechnology}{Haringhata, West Bengal, India}
     \resumeSubheading
        {Ramakrishna Mission Vivekananda Centenary College}{July 2016 -- October 2020}
        {BSc in Zoology}{Khardaha, West Bengal, India}    

\resumeSubHeadingListEnd


%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
% this section can include experience gained in coursework, or group or independent research projects
% delete or add Subheading sections as needed
\resumeSubHeadingListStart

\resumeSubheading
% list month-year for the start date followed by month-year for the end date (or "Present" if ongoing)
        {Evolution of resistance under divergent rate of pathogen
selection}{}
        {Ashoka University, Sonepat, Haryana, India (February 2022 -- June 2022)}{}
      \resumeItemListStart
        \resumeItem{This was my MSc dissertation thesis. I did some experiments to check the rate of evolution of resistance against different pathogens in Tribolium beetles.}
    \resumeItemListEnd
\resumeSubheading   
        {COPD: Making Sense of Existing GWAS Findings in Indian Context}{}
        {MAKAUT, WB, Haringhata, India (December 2021 - February 2022)}{}
      \resumeItemListStart
        \resumeItem{It was a small research project during my MSc, We jotted down the genes and SNPs responsible for COPD in the Indian population from 1456 variants \& did pathway analysis to check their functions that might be relevant for COPD development.}
    \resumeItemListEnd
\resumeSubheading   
        {Temporal diversity of urban butterflies: A case study}{}
        {RKMVC College, Khardaha, WB, India (November 2016 - January 2020)}{}
      \resumeItemListStart
        \resumeItem{I did this project during my BSc. We sampled butterflies in and around our college campus. We did a checklist of butterflies and also observed how their community is changing across seasons with vegetation pattern.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


% OPTIONAL SECTION : DELETE FROM HERE UNTIL % % % % TO REMOVE
%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
% if you have been employed, do volunteer activities, or have held other formal or informal jobs, you can list them here.   
\resumeSubHeadingListStart

    \resumeSubheading
% list month-year for the start date followed by month-year for the end date (or "Present" if ongoing)
        {Graduate Teaching Assistant}{August 2023  -- Present}
        {Department of Biology, Texas A\& M University}{College Station, TX, USA}
      \resumeItemListStart

        \resumeItem{I have taught the lab courses of BIOL 111 (Introductory Biology) in Fall 2023. I am teaching BIOL 112 in Spring 2024 as well. This role requires me to give a background of the topic of the lab to the undergraduate students, supervise them while they are doing their lab exercises, grade their laboratory assignments, set up questions for Lab exams and grading them.}

        \resumeItemListEnd

    \resumeSubheading
      {Project Assistant}{July 2022 -- March 2023}
      {Evolutionary Immunology Lab, Ashoka University}{Sonepat, Haryana, India}
      \resumeItemListStart
        \resumeItem{I studied sperm competition abilities of Tribolium beetles and the role of chronic malnutrition in disease transmission in Drosophila as a research assistant after completing my MSc. This position required me to do experiments, record, analyze and present data \& maintain populations of the model organisms.}
    
        \resumeItemListEnd

\resumeSubHeadingListEnd
% % % % END OPTIONAL SECTION PROFESSIONAL EXPERIENCE % % % %


% OPTIONAL SECTION : DELETE FROM HERE UNTIL % % % % TO REMOVE 
%-----------SKILLS-----------
\section{Skills}
% This section can include programming or spoken languages, text editing and general software knowledge, certifications, version control or project management tools, or other skills that might be relevant. You can include as many or as few as you like: delete or add as needed.  
\begin{itemize}[leftmargin=0.15in, label={}]
    \normalsize{\item{
     \textbf{Computer Languages}{: R (intermediate), Python (beginner), Bash (beginner), HTML(intermediate)} \\
     \textbf{Wet Lab techniques}{: Ultracentrifuge, DNA extraction, RNA extraction, PCR, electrophoresis, spectrophotometer, high resolution camera operated microscope, basic microbial techniques, field sampling techniques}\\
     \textbf{Softwares}{: Basic computer applications like Microsoft Office, SPSS, PAST, different bioinformatic tools} \\
     \textbf{Other skills}{: Digital photography and photo editing, digital art} \\
    }}
 \end{itemize}
% % % % END OPTIONAL SECTION SKILLS % % % %
% OPTIONAL SECTION : DELETE FROM HERE UNTIL % % % % TO REMOVE
%-----------RESEARCH PRESENTATIONS-----------
\section{Presentations} 
% It is not expected that applicants will have items for this section, but if you have presented or published research findings, you are welcome to include them here

    \normalsize{{
    \begin{itemize}
        \item { 4th Annual Conference of the Indian Society for Evolutionary Biologists, ‘Revolutionising Darwinian Synthesis: Fresh Perspectives and Future Challenges.’, (\textit{02/09/2023-02/11/2023, Ahmedabad, India)}}{\textbf{ Poster}} \\
    \end{itemize}
    \begin{itemize}
        \item {Manufacturing (Level 1) \& COVID-Food Safety Supervisor, \textit{(02/20/2021-02/21/2021, Kolkata, India)}}{\textbf{ Poster}[Won technical brilliance award]}
    \end{itemize}
    \begin{itemize}
        \item {6th Asian Lepidoptera Conservation Symposium, \textit{(09/17/2019-09/21/2019, Kolkata, India)}}{\textbf{ Poster}}
    \end{itemize}
    \begin{itemize}
        \item {ALLERCON-2017, The 7th National Conference on Respiratory Allergy and Immunology, \textit{(01/14/2018, Kolkata, India)}}{\textbf{ Poster}[Won best presenter award]}
    \end{itemize}
    \begin{itemize}
        \item {National Conference on Status of Invasive Alien Species in India, \textit{(12/14/2017-12/15/2017, Kolkata, India)}}{\textbf{ Poster}}
    \end{itemize}
    \begin{itemize}
        \item {National Seminar on Forest Resources: Conservation Issues and Management, \textit{(09/09/2017, Kolkata, India)}}{\textbf{ Poster}}
    \end{itemize}
}}

% % % % END OPTIONAL SECTION RESEARCH PRESENTATIONS % % % %

% OPTIONAL SECTION : DELETE FROM HERE UNTIL % % % % TO REMOVE 
%-----------Certifications-----------
\section{Certifications} 
% This section can include academic achievements and honors as well as recognition in your community. Remove or add sections as needed.
\resumeSubHeadingListStart
    \resumeSubheading
    {AI0101EN: AI for Everyone: Master the Basics}{4 weeks}
    {Certificate ID: \href{https://courses.edx.org/certificates/6fd8789d1ae146348a4bda736f3696d6}{6fd8789d1ae146348a4bda736f3696d6}}{Platform: edX}
    \resumeSubheading
    {PY0101EN: Python Basics for Data Science}{5 weeks}
    {Certificate ID: \href{https://courses.edx.org/certificates/5cc9d19334e94a9682fa0bc969f726c0}{5cc9d19334e94a9682fa0bc969f726c0}}{Platform: edX}
    \resumeSubheading
    {PH125.2x: Data Science: Visualization}{8 weeks}
    {Certificate ID: \href{https://courses.edx.org/certificates/a40f449f0e534960b7ef8fe3f572ed56}{a40f449f0e534960b7ef8fe3f572ed56}}{Platform: edX}
    \resumeSubheading
    {LFS101x: Introduction to linux}{14 weeks}
    {Certificate ID: \href{https://courses.edx.org/certificates/4a6c484ebde6412cb68fba71e4ba2828}{4a6c484ebde6412cb68fba71e4ba2828}}{Platform: edX}
\resumeSubHeadingListEnd

% % % % END OPTIONAL SECTION CERTIFICATIONS % % % %

% OPTIONAL SECTION : DELETE FROM HERE UNTIL % % % % TO REMOVE 
%-----------Publications-----------
\section{Publications} 
\begin{itemize}
        \item {Dutta, T., \textbf{Bhattacharya, A.} 2022. Chronic Obstructive Pulmonary Disease (COPD): Making
Sense of Existing GWAS Findings in Indian Context. \textit{Int J Biomed Clin Anal.}, \textbf{2(1)}:29-37}
    \end{itemize}
    \begin{itemize}
        \item {\textbf{Bhattacharya, A.}, Chakraborty, S., Das, K.L., Saha, A., Sardar,S., Mandal, B., Murkherjee, A.
and Mitra, B. 2018. Temporal diversity of urban butterflies: A case study in the campus of
Ramakrishna mission Vivekananda centenary College, Rahara, West Bengal. \textit{The Pharma
Innovation Journal}, \textbf{7(12)}: 395-400.}
    \end{itemize}
    
% % % % END OPTIONAL SECTION PUBLICATIONS % % % %

% OPTIONAL SECTION : DELETE FROM HERE UNTIL % % % % TO REMOVE 
%-----------Publications in Abstracts-----------
\section{Publications in abstracts} 
\begin{itemize}
        \item {\textbf{Bhattacharya, A.}, Bose, J., Khan, I. 2023/09/02 to 2023/11/02. Linking evolution under chronic malnutrition, costs of infection and disease transmission. \textit{4th Annual Conference, Indian Society of Evolutionary Biologists, ‘Revolutionising Darwinian Synthesis: Fresh Perspectives and Future Challenges.’} Pp- 87}
    \end{itemize}
\begin{itemize}
        \item {\textbf{Bhattacharya, A.}, Das, S., Ghosh, D., Sardar, S., Mandal, B., Mukherjee, A., Mitra, B. 2019/17/09 to 2019/21/09. Community foraging of butterflies on \textit{Lantana camara} –
partition or overlapping. \textit{6th Asian Lepidoptera Conservation symposium}. Pp- 90}
    \end{itemize}
\begin{itemize}
        \item {\textbf{Bhattacharya, A.}, Chakraborty, S., Das, K.L., Sardar,S., Mandal, B. and Murkherjee, A.
2018/14/01. Alternative proposal for combating the pollen-induced allergy by introducing
non allergic butterfly parks in urban area- a case study. \textit{ALLERCON-2017, The 7th
National Conference on Respiratory Allergy and Immunology.} Pp-36}
    \end{itemize}
\begin{itemize}
        \item {Chakraborty, S., Das, K.L., \textbf{Bhattacharya, A.}, Saha, A., Sardar,S., Mandal, B. and Murkherjee, A. 2017/14/12 \& 2017/15/12. Temporal shifting in communities of butterflies in a suburban area and it’s relation with social plantation. \textit{National Conference on Status of Invasive Alien Species in India.} Pp-59.}
    \end{itemize}
\begin{itemize}
        \item {\textbf{Bhattacharya, A.}, Saha, A., Chakraborty, S., Das, K.L., Sardar,S., Mandal, B. and
Murkherjee, A. 2016/09/09. Small scale social foresting in suburban area for upholding
the temporal variations of butterflies. \textit{Nat. Sem. On Forest Resources: Conser. Issues
and Mgmt.} Pp- 30.}
    \end{itemize}
   % % % % END OPTIONAL SECTION ABSTRACTS % % % % 


% OPTIONAL SECTION : DELETE FROM HERE UNTIL % % % % TO REMOVE 
%-----------GRANTS-----------
\section{Grants}
% Also an optional section, for any hobbies, sports, artistic and musical pursuits, etc. that you would like to include. You can include as many or as few as you like: delete or add as needed. 
\begin{itemize}[leftmargin=0.15in, label={}]
    \normalsize{\item{
     \textbf{EKTA Incubation Centre-TBI (MAKAUT,WB)}{: {45000INR for ecological restoration. \textit{(Declined)}} } \\
    }}    
 \end{itemize}
% % % % END OPTIONAL SECTION GRANTS % % % %

\end{document}
